Bioverse: The Habitable Zone Inner Edge Discontinuity as an Imprint of Runaway Greenhouse Climates on Exoplanet Demographics

### 2023-05-11 src/tex/ms.tex
acknowledge discussions at AstroBio23

\begin{acknowledgments}
The authors thank Gabriele Cugno, Yann Fabel, Brad Foley, Megan Mansfield, Paul Molliere, Gijs Mulders, Matthew Murphy, and Terry-Ann Suer for insightful discussions.
We are grateful to Martin Turbet for providing the mass-radius relationship data for planets harboring steam atmospheres.
This material is based upon work supported by the National Aeronautics and Space Administration under Agreement No. 80NSSC21K0593 for the program ``Alien Earths''.
The results reported herein benefitted from collaborations and/or information exchange within NASA’s Nexus for Exoplanet System Science (NExSS) research coordination network sponsored by NASA’s Science Mission Directorate.
This work has made use of data from the European Space Agency (ESA) mission \gaia\ (\url{https://www.cosmos.esa.int/gaia}), processed by the \gaia\ Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the \gaia\ Multilateral Agreement.
T.L. was supported by a grant from the Branco Weiss Foundation.
G.B. acknowledges support from the NASA Astrophysics Data Analysis Program under Grant No.~80NSSC20K0446.
A.S. acknowledges support from NASA's Habitable Worlds Program (No.~80NSSC20K0226).
\end{acknowledgments}

>>>>

\begin{acknowledgments}
The authors thank Gabriele Cugno, Yann Fabel, Brad Foley, Lisa Kaltenegger, Ravi Kopparapu, Eric Mamajek, Megan Mansfield, Paul Molliere, Gijs Mulders, Matthew Murphy, Sukrit Ranjan, and Terry-Ann Suer for insightful discussions.
We are grateful to Martin Turbet for providing the mass-radius relationship data for planets harboring steam atmospheres.
This material is based upon work supported by the National Aeronautics and Space Administration under Agreement No. 80NSSC21K0593 for the program ``Alien Earths''.
The results reported herein benefitted from collaborations and/or information exchange within NASA’s Nexus for Exoplanet System Science (NExSS) research coordination network sponsored by NASA’s Science Mission Directorate.
This work has made use of data from the European Space Agency (ESA) mission \gaia\ (\url{https://www.cosmos.esa.int/gaia}), processed by the \gaia\ Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the \gaia\ Multilateral Agreement.
T.L. was supported by a grant from the Branco Weiss Foundation.
G.B. acknowledges support from the NASA Astrophysics Data Analysis Program under Grant No.~80NSSC20K0446.
A.S. acknowledges support from NASA's Habitable Worlds Program (No.~80NSSC20K0226).
\end{acknowledgments}
